### 2016-02-11 inputs/results.tex
new table with accuracies
new table for accuracies

In rice, the average imputation accuracy over all genotype classes was above 80\% for all methods. No significant difference was found between chromosomes. Thus average accuracy over all chromosomes is therefore presented (Figure~\ref{fig:accuracy_rice}). \\
The overall accuracy for alfalfa, averaged across the two datasets, was 12-25\% lower than rice, ranging between 66\% and 84\%. No significant differences were found between the two datasets. Thus average accuracy over the Alfalfa-Med and Alfalfa-PV is presented (Figure~\ref{fig:accuracy_alfalfa}).

The imputation accuracy varied across the different genotype classes, with the highest accuracy in the most common genotype (averaging 92.27\% and 96.47\% in alfalfa and rice, respectively), while the least common genotype class showed much lower accuracy (averaging 5.79\% and 69.88\% in alfalfa and rice, respectively).
Alfalfa datasets included heterozygous SNP loci, accounting for an average of 27\% of individuals per locus (Table~\ref{tab:descriptive_statistics}). Heterozygotes had an intermediate imputation accuracy ranging from 0\% with MNI to 70\% with KNNI. Results for each individual alfalfa population and the 12 individual rice chromosomes are similar to those discussed here (see Supplementary Figures S2 to S15). \\
Missing rate did not affect the imputation accuracy substantially, with most algorithms showing a flat or almost flat response to increased missing rate. KNNI showed a decreasing imputation accuracy with increasing missing rate, both in alfalfa and rice.

Beagle outperformed all other imputation methods in rice, making efficient use of marker position (Figure~\ref{fig:accuracy_rice}). When markers were randomly reshuffled (thus offsetting position information), though, general imputation methods (other than MNI) showed a higher imputation accuracy than Beagle. The accuracy loss with shuffled markers is exacerbated in alfalfa datasets, and in particular in heterozygous and minor homozygous genotypes.\\
Similarly, FILLIN resulted in a 5-10\% accuracy drop when marker positions were shuffled. FILLIN performances were in general lower than other methods due to the fraction of unimputed genotypes, here accounted as imputation errors. On average, FILLIN did not impute 14.6\% of missing data in Rice and practically the entirety of Alfalfa data. Even trying to relax FILLIN parameters, it was impossible to obtain sensible results in alfalfa. Thus, FILLIN accuracy results are not reported in Figure~\ref{fig:accuracy_alfalfa}.

When examining general imputation methods, resulting accuracies highlighted RFI and KNNI as the best ones. The two methods had comparable performances over all experiments. SVDI followed, and MNI ranked last.\\
In Rice, for 70\% allowed missing rate, the imputation accuracy of RFI was still higher than 90\%, while it dropped towards 85\% for KNNI and SVDI. As expected, MNI had an imputation accuracy of 100\% in the major homozygous class, but dropped to 0\% in the minor homozygous class.\\
In alfalfa KNNI showed the highest imputation accuracy over all classes (averaging 82.20\%) and in the heterozygous (66.02\%) and minor homozygous (14.68\%) genotype classes (Figure~\ref{fig:accuracy_alfalfa}). RFI and SVDI were second ranking. They did not differ much from MNI in the overall accuracy (MNI: 78.38\%, RFI: 79.50\%, SVDI: 77.35\%) and in the major (MNI: 88.68\%, RFI: 89.05\%, SVDI 85.81\%) homozygous class, but gave higher imputation accuracy in the heterozygous (MNI: 58.87\%, RFI: 61.75\%, SVDI 61.67\%). In the minor homozygous class only SVDI resulted in some sporadic correct imputation, while RFI and MNI did not produce any sensible result (MNI: 0\%, RFI: 0.01\%, SVDI 4.46\%) classes.

>>>>

\input{inputs/table_accuracies}

In rice, the average imputation accuracy over all genotype classes was above 80\% for all methods. No significant difference was found between chromosomes. Thus average accuracy over all chromosomes is therefore presented (Figure~\ref{fig:accuracy_rice}). \\
The overall accuracy for alfalfa, averaged across the two datasets, was 12-25\% lower than rice, ranging between 66\% and 82\%. No significant differences were found between the two datasets. Thus average accuracy over the Alfalfa-Med and Alfalfa-PV is presented (Figure~\ref{fig:accuracy_alfalfa}).

The imputation accuracy varied across the different genotype classes, with the highest accuracy in the most common genotype (averaging 92.27\% and 96.47\% in alfalfa and rice, respectively), while the least common genotype class showed much lower accuracy (averaging 5.79\% and 69.88\% in alfalfa and rice, respectively).
Alfalfa datasets included heterozygous SNP loci, accounting for an average of 27\% of individuals per locus (Table~\ref{tab:descriptive_statistics}). Heterozygotes had an intermediate imputation accuracy ranging from 0.5\% with Beagle to 66.03\% with KNNI. Results for each individual alfalfa population and the 12 individual rice chromosomes are similar to those discussed here (see Supplementary Figures S2 to S15). \\
Missing rate did not affect the imputation accuracy substantially, with most algorithms showing a flat or almost flat response to increased missing rate. KNNI showed a decreasing imputation accuracy with increasing missing rate, both in alfalfa and rice.

Beagle outperformed all other imputation methods in rice, making efficient use of marker position (Figure~\ref{fig:accuracy_rice}). When markers were randomly reshuffled (thus offsetting position information), though, general imputation methods (other than MNI) showed a higher imputation accuracy than Beagle. The accuracy loss with shuffled markers is exacerbated in alfalfa datasets, and in particular in heterozygous and minor homozygous genotypes.\\
Similarly, FILLIN resulted in a 5-8\% accuracy drop when marker positions were shuffled. FILLIN performances were in general lower than other methods due to the fraction of unimputed genotypes, here accounted as imputation errors. On average, FILLIN did not impute 14.6\% of missing data in Rice and practically the entirety of Alfalfa data. Even trying to relax FILLIN parameters, it was impossible to obtain sensible results in alfalfa. Thus, FILLIN accuracy results are not reported in Figure~\ref{fig:accuracy_alfalfa}.

When examining general imputation methods, resulting accuracies highlighted RFI and KNNI as the best ones. The two methods had comparable performances over all experiments. SVDI followed, and MNI ranked last.\\
In Rice, for 70\% allowed missing rate, the imputation accuracy of RFI was still higher than 90\%, while it dropped towards 85\% for KNNI and SVDI. As expected, MNI had an imputation accuracy of 100\% in the major homozygous class, but dropped to 0\% in the minor homozygous class.\\
In alfalfa KNNI showed the highest imputation accuracy over all classes (averaging 82.20\%) and in the heterozygous (66.03\%) and minor homozygous (14.68\%) genotype classes (Figure~\ref{fig:accuracy_alfalfa}). RFI and SVDI were second ranking. They did not differ much from MNI in the overall accuracy (MNI: 78.38\%, RFI: 79.50\%, SVDI: 77.36\%) and in the major (MNI: 88.69\%, RFI: 89.05\%, SVDI 85.81\%) homozygous class, but gave higher imputation accuracy in the heterozygous (MNI: 58.88\%, RFI: 61.75\%, SVDI 61.67\%). In the minor homozygous class only SVDI resulted in some sporadic correct imputation, while RFI and MNI did not produce any sensible result (MNI: 0\%, RFI: 0.01\%, SVDI 4.47\%) classes.

### 2016-02-11 inputs/table_accuracies.tex
new table for accuracies

\begin{table}
\centering
\caption[Accuracy statistics]{some long caption}
\label{tab:accuracy_statistics}
\begin{tabular}{llcccc}
\hline\noalign{\smallskip}
\noalign{\smallskip}\hline\noalign{\smallskip}
\textbf{Dataset} & \textbf{Method} & \textbf{Total} & \textbf{Minor (BB)} & \textbf{Major (AA)} & \textbf{Heterozygote (AB)}\\
\noalign{\smallskip}\Xhline{3\arrayrulewidth}\noalign{\smallskip}
alfalfa & Beagle & 73.14 & 14.27 & 99.37 & 20.77\\
alfalfa & Beagle (shuffle) & 66.34 & 1.31 & 99.88 & 0.50\\
alfalfa & kNNI & 82.20 & 14.68 & 90.82 & 66.03\\
alfalfa & MNI & 78.38 & 0.00 & 88.69 & 58.88\\
alfalfa & RFI  & 79.50 & 0.00 & 89.05 & 61.75\\
alfalfa & SVDI & 77.36 & 4.47 & 85.81 & 61.67\\
alfalfa & FILLIN & * & * & * & *\\
alfalfa & FILLIN (shuffle)  & * & * & * & *\\
rice (chr) & Beagle & 99.58 & 97.50 & 99.80 & -\\
rice (chr) & Beagle (shuffle) & 96.09 & 74.73 & 98.42 & -\\
rice (chr) & kNNI & 98.10 & 89.12 & 99.04 & -\\
rice (chr) & MNI & 90.19 & 1.06 & 99.89 & -\\
rice (chr) & RFI  & 98.81 & 91.51 & 99.58 & -\\
rice (chr) & SVDI & 97.81 & 85.64 & 99.11 & -\\
rice (chr) & FILLIN & 86.96 & 63.62 & 90.14 & -\\
rice (chr) & FILLIN (shuffle)  & 82.19 & 55.86 & 85.81 & -\\
rice & Beagle & 99.58 & 97.57 & 99.80 & -\\
rice & Beagle (shuffle) & 93.48 & 55.64 & 97.69 & -\\
rice & kNNI & 98.30 & 89.80 & 99.19 & -\\
rice & MNI & 90.21 & 0.61 & 99.89 & -\\
rice & RFI  & 97.86 & 84.68 & 99.28 & -\\
rice & SVDI & 95.74 & 70.96 & 98.40 & -\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Accuracy statistics]{Imputation accuracies (as percentages) for the various
datasets and methods, averaged over all allowed and injected missing thresholds. Rice data are reported averaged by chromosome and on the complete genotypes. Alfalfa data are reported averaged over the two Alfalfa-PV and Alfalfa-Med populations. FILLIN failed to impute alfalfa datasets.}
\label{tab:accuracy_statistics}
\begin{tabular}{llcccc}
\hline\noalign{\smallskip}
\noalign{\smallskip}\hline\noalign{\smallskip}
\textbf{Dataset} & \textbf{Method} & \textbf{Total} & \textbf{Minor (BB)} & \textbf{Major (AA)} & \textbf{Heterozygote (AB)}\\
\noalign{\smallskip}\Xhline{3\arrayrulewidth}\noalign{\smallskip}
alfalfa & Beagle & 73.14 & 14.27 & 99.37 & 20.77\\
alfalfa & Beagle (shuffle) & 66.34 & 1.31 & 99.88 & 0.50\\
alfalfa & kNNI & 82.20 & 14.68 & 90.82 & 66.03\\
alfalfa & MNI & 78.38 & 0.00 & 88.69 & 58.88\\
alfalfa & RFI  & 79.50 & 0.01 & 89.05 & 61.75\\
alfalfa & SVDI & 77.36 & 4.47 & 85.81 & 61.67\\
alfalfa & FILLIN & * & * & * & -\\
alfalfa & FILLIN (shuffle)  & * & * & * & -\\
rice (chr) & Beagle & 99.58 & 97.50 & 99.80 & -\\
rice (chr) & Beagle (shuffle) & 96.09 & 74.73 & 98.42 & -\\
rice (chr) & kNNI & 98.10 & 89.12 & 99.04 & -\\
rice (chr) & MNI & 90.19 & 1.06 & 99.89 & -\\
rice (chr) & RFI  & 98.81 & 91.51 & 99.58 & -\\
rice (chr) & SVDI & 97.81 & 85.64 & 99.11 & -\\
rice (chr) & FILLIN & 86.96 & 63.62 & 90.14 & -\\
rice (chr) & FILLIN (shuffle)  & 82.19 & 55.86 & 85.81 & -\\
rice & Beagle & 99.58 & 97.57 & 99.80 & -\\
rice & Beagle (shuffle) & 93.48 & 55.64 & 97.69 & -\\
rice & kNNI & 98.30 & 89.80 & 99.19 & -\\
rice & MNI & 90.21 & 0.61 & 99.89 & -\\
rice & RFI  & 97.86 & 84.68 & 99.28 & -\\
rice & SVDI & 95.74 & 70.96 & 98.40 & -\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
